Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
add comments
review results

%---------------------------------
\subsection{Results}
\label{experimental-results}

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples  and fixed point precision increases. However, two benchmarks in our set
did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.

@@

We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the 12 out of 15 benchmarks, and can be
complemented using the interval arithmetic back-end for 2 additional benchmarks,
where the inductive conjectures fail too frequently. Both back-ends together enabled controller
synthesis for 14 out of 15 benchmarks within reasonable time frames. \pksay{TODO: Upload full
experiments environment including README and result log files to anonymous Google Drive and
provide link here.}

>>>>

%---------------------------------
\subsection{Results}
\label{experimental-results}
%---------------------------------

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}) \textcolor{red}{Pascal: Why they did not meet the criteria?}. 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes \textcolor{red}{Pascal: Why is it slower?}.

\textcolor{red}{Pascal: Can you please add FWL for each synthesized controller using the following format <I,F>, where I represents the number of bits in the integer part and F represents the number of bits in the fractional part?}

@@

We conclude from these results that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks within reasonable time frames. \textcolor{red}{Why do we fail to synthesise 1 controller?} 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}
